---
title: 'Example Dashboard'
author: "Bryce Murphy"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    orientation: rows
    vertical_layout: fill
runtime: shiny
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(DT)
library(shiny)
library(flexdashboard)
library(lubridate)
library(janitor)
library(RCurl)
library(gridExtra)
```


<!-- WELLNESS DATA -->
```{r message = FALSE, echo = FALSE}


path <- getURL("https://raw.githubusercontent.com/bryce-murphy/usoc_example/master/mock_wellness.csv")
wellness <- read_csv(path)

path_2 <- getURL("https://raw.githubusercontent.com/bryce-murphy/usoc_example/master/mock_load.csv")
training <- read_csv(path_2)


                                                                ##### DATA CLEANING #####
# Change date to a date format using lubridate
wellness$Date <- mdy(wellness$Date)
wellness$Weekday <- weekdays(wellness$Date)


# Fix the 0's in the scale
wellness_gather <-
  wellness %>%
  gather(key = wellness_var, value = measurement, -c(Date, Athlete, Team, Weekday))

# Take the average of duplicate athletes on the same day
wellness <- 
  wellness_gather %>%
  group_by(Date, Athlete, Team, Weekday, wellness_var) %>%
  summarise_at(vars(matches("measurement")), mean) %>%
  ungroup() %>%
  spread(key = wellness_var, value = measurement)
  

# Create the scaled values by athlete
wellness_clean <-
  wellness %>%
  clean_names() %>%
  mutate(sleep_load = sleep_hours * sleep_quality,
         sleep_quality_z = round(ave(sleep_quality, athlete, FUN = scale), digits = 2),
         mood_z = round(ave(mood, athlete, FUN = scale), digits = 2),
         readiness_to_train_z = round(ave(readiness_to_train, athlete, FUN = scale), digits = 2),
         soreness_z = round(ave(soreness, athlete, FUN = scale), digits = 2),
         stress_z = round(ave(stress, athlete, FUN = scale), digits = 2),
         fatigue_z = round(ave(fatigue, athlete, FUN = scale), digits = 2),
         sleep_hours_z = round(ave(sleep_hours, athlete, FUN = scale), digits = 2)) %>%
  group_by(athlete) %>%
  mutate(daily_wellness = (sleep_quality + mood + readiness_to_train + soreness + stress + fatigue)/6,
         daily_wellness = round(daily_wellness, digits = 2),
         daily_wellness_z = round(ave(daily_wellness, athlete, FUN = scale), digits = 2))

wellness_clean[is.na(wellness_clean)] <- 0

# Create colors that will be used for wellness alerts
wellness_clean$zcolors <- sapply(1:length(wellness_clean$daily_wellness_z), function(i) {
  
  if (is.na(wellness_clean$daily_wellness_z[i]))
    return(NA)
  
  if (abs(wellness_clean$daily_wellness_z[i]) <= 1.5) {
    return("green")
  } else if (abs(wellness_clean$daily_wellness_z[i]) >= 2) {
    return("red")
  } else {
    return("yellow")
  }
})

alert <- 
  wellness_clean %>%
  select(date, athlete, sleep_quality_z, mood_z, readiness_to_train_z, soreness_z, stress_z, fatigue_z) %>%
  gather(key = wellness_var, value = z_score, -c(date, athlete))

```

<!-- TRAINING LOAD DATA -->
``` {r message = FALSE, echo = FALSE}

training$Date <- mdy(training$Date)
training$Weekday <- weekdays(training$Date)

training_gather <-
  training %>%
  gather(key = training_var, value = measurement, -c(1:11, 30))

# Fix duplicates
training <-
  training_gather %>%
  group_by(Athlete, Date, Weekday, Team, `Injury/Illness Status`, `Training Availability`, `Injury First Time Report`,
           `Injury Type`, `Training/NoTraining`, `Training Location`, `Travel/No Travel`, `Recovery Modality`, training_var) %>%
  summarise_at(vars(matches("measurement")), mean) %>%
  ungroup() %>%
  spread(key = training_var, value = measurement)
  

training_clean <-
  training %>%
  clean_names() %>%
  mutate_if(is.integer, replace_na, 0) %>%
  mutate(competition_load_z = round(ave(competition_load, athlete, FUN = scale), digits = 2),
         conditioning_load_z = round(ave(conditioning_load, athlete, FUN = scale), digits = 2),
         practice_load_z = round(ave(practice_load, athlete, FUN = scale), digits = 2),
         strength_load_z = round(ave(strength_load, athlete, FUN = scale), digits = 2)) %>%
  mutate_at(.vars = c("competition_load_z", "conditioning_load_z", "practice_load_z", "strength_load_z"), replace_na, 0)
    
        
```

Team Overview
==================================

Column {.sidebar}
----------------------------------

### Choose Date: {data-height=100}
```{r echo = FALSE}

latest_wellness_date <- max(wellness_clean$date)

wellness_date_format <- "%b %d %Y"

wellness_clean <-
  wellness_clean %>%
  arrange(desc(wellness_clean$date))

selectInput("date",
          label = NULL,
          choices = wellness_clean$date,
          selected = format(latest_wellness_date, 
                            format = wellness_date_format))


```

```{r include=FALSE}

wellness_date <-
  reactive({
  mdy(input$date)
  
})
```

### Wellness Alert(s) 
### < 1.5 {data-height=200}
```{r echo = FALSE}


renderPrint({

alert <- 
  wellness_clean %>%
  filter(date == input$date) %>%
  select(date, athlete, sleep_quality_z, mood_z, readiness_to_train_z, soreness_z, stress_z, fatigue_z, sleep_hours_z) %>%
  gather(key = wellness_var, value = z_score, -c(date, athlete))

for (i in 1:length(alert$athlete)) {
   if (alert$z_score[[i]] < -1.5) {
  print(paste(alert$athlete[[i]], "-", alert$wellness_var[[i]]))
 } 
}

})

```

### High Load Alert(s)
```{r echo = FALSE}

renderPrint({
  
  alert <- 
    training_clean %>%
    filter(date == input$date) %>%
    select(date, athlete, competition_load_z, conditioning_load_z, practice_load_z, strength_load_z) %>%
    gather(key = training_var, value = z_score, -c(date, athlete))
  
  for (i in 1:length(alert$athlete)) {
   if (alert$z_score[[i]] > 1.5) {
  print(paste(alert$athlete[[i]], "-", alert$training_var[[i]]))
 } 
}
    
})

```


### Low Load Alert(s)
```{r echo = FALSE}

renderPrint({
  
  alert <- 
    training_clean %>%
    filter(date == input$date) %>%
    select(date, athlete, competition_load_z, conditioning_load_z, practice_load_z, strength_load_z) %>%
    gather(key = training_var, value = z_score, -c(date, athlete))
  
  for (i in 1:length(alert$athlete)) {
   if (alert$z_score[[i]] < -1.5) {
  print(paste(alert$athlete[[i]], "-", alert$training_var[[i]]))
 } 
}
    
})

```

### Injury Alert(s)
```{r echo = FALSE}

renderPrint({
  
  alert <- 
    training_clean %>%
    filter(date == input$date) %>%
    select(date, athlete, injury_illness_status, training_availability, injury_type, injury_illness_status) 
  
  for (i in 1:length(alert$athlete)) {
   if (alert$training_availability[[i]] < 100) {
  print(paste(alert$athlete[[i]], "-", alert$injury_illness_status[[i]])) 
     
   }
  }
 
  for (i in 1:length(alert$athlete)) {
    if (alert$injury_illness_status[[i]] == "New Injury") {
   print(paste(alert$athlete[[i]], "-", alert$injury_type[[i]]))
    }
  }
  
})

```

Row
----------------------

### Wellness


```{r echo = FALSE}


renderPlot({
  
team_wellness <- 
  wellness_clean %>%
  group_by(team, date) %>%
  summarise(sleep_hours = round(mean(sleep_hours), digits = 2),
            `Sleep Quality` = round(mean(sleep_quality_z), digits = 2),
            Mood = round(mean(mood_z), digits = 2),
            `Readiness to Train` = round(mean(readiness_to_train_z), digits = 2),
            Soreness = round(mean(soreness_z), digits = 2),
            Stress = round(mean(stress_z), digits = 2),
            Fatigue = round(mean(fatigue_z), digits = 2),
            `Daily Wellness` = round(mean(daily_wellness_z), digits = 2))

team_wellness$zcolors <- sapply(1:length(team_wellness$`Daily Wellness`), function(i) {
  
  if (is.na(team_wellness$`Daily Wellness`[i]))
    return(NA)
  
  if (abs(team_wellness$`Daily Wellness`[i]) <= 1.5) {
    return("green")
  } else if (abs(team_wellness$`Daily Wellness`[i]) >= 2) {
    return("red")
  } else {
    return("yellow")
  }
})
  
  # Team 1 Data
  team_1_wellness <-
    team_wellness %>%
    filter(team == "Team 1",
           date == input$date) %>%
    gather(key = wellness_var, value = z_score, -c(team, date, zcolors, sleep_hours))
  
  # Reorder by z score
  team_1_wellness$wellness_var <- reorder(team_1_wellness$wellness_var, -team_1_wellness$z_score)
  
  plot_1 <-  ggplot(team_1_wellness, aes(x = wellness_var, y = z_score, fill = z_score)) +
      geom_bar(stat = "identity", color = "black") +
      scale_fill_identity() +
      geom_rect(aes(ymin = -Inf, ymax = -1.5, xmin = -Inf, xmax = Inf), fill = "pink", alpha = 1/100) +
      geom_rect(aes(ymin = -1.5, ymax = 0, xmin = -Inf, xmax = Inf), fill = "yellow", alpha = 1/100) +
      geom_rect(aes(ymin = 0, ymax = Inf, xmin = -Inf, xmax = Inf), fill = "green", alpha = 1/100) +
      scale_fill_gradient2(low = "red", mid = "yellow", high = "green", midpoint = 0, limits = c(-3.0, 3.0), guide = F) +
      theme_minimal() +
      labs(title = "Daily Wellness - Team 1",
           y = "Scaled Wellness < 0 is below their average",
           x = "") +
      coord_flip()
    
  #   # Set ordering by daily_wellness_z
  # daily_data$Name <- reorder(daily_data$Name, -daily_data$Well_S)
    
    # Team 2 Data
     team_2_wellness <-
    team_wellness %>%
    filter(team == "Team 2",
           date == input$date) %>%
    gather(key = wellness_var, value = z_score, -c(team, date, zcolors, sleep_hours))
  
  # Reorder by z score
  team_2_wellness$wellness_var <- reorder(team_2_wellness$wellness_var, -team_2_wellness$z_score)
  
  plot_2  <- 
    ggplot(team_2_wellness, aes(x = wellness_var, y = z_score, fill = z_score)) +
      geom_bar(stat = "identity", color = "black") +
      scale_fill_identity() +
      geom_rect(aes(ymin = -Inf, ymax = -1.5, xmin = -Inf, xmax = Inf), fill = "pink", alpha = 1/100) +
      geom_rect(aes(ymin = -1.5, ymax = 0, xmin = -Inf, xmax = Inf), fill = "yellow", alpha = 1/100) +
      geom_rect(aes(ymin = 0, ymax = Inf, xmin = -Inf, xmax = Inf), fill = "green", alpha = 1/100) +
      scale_fill_gradient2(low = "red", mid = "yellow", high = "green", midpoint = 0, limits = c(-3.0, 3.0), guide = F) +
      theme_minimal() +
      theme(axis.text.y = element_blank()) +
      labs(title = "Daily Wellness - Team 2",
           y = "Scaled Wellness < 0 is below their average",
           x = "") +
      coord_flip()
    
  
 grid.arrange(plot_1, plot_2, ncol = 2)
  
})
    
```


Row
------------------------------

```{r echo = FALSE}

DT::renderDataTable({

  table <-
    wellness_clean %>%
    filter(date == input$date) %>%
    select(athlete, team, fatigue, mood, readiness_to_train, sleep_hours, sleep_quality, soreness)

  datatable(table, filter = "top", options = list(pageLength = 5),
            colnames = c("Athlete" = 2, "Team" = 3, "Fatigue" = 4, "Mood" = 5, "Readiness to Train" = 6,
                         "Sleep Hours" = 7, "Sleep Quality" = 8, "Soreness" = 9))

})

```

Individual 
==================================


Column {.sidebar}
----------------------------------

### Choose Date: {data-height=100}
```{r echo = FALSE}

latest_wellness_date <- max(wellness_clean$date)
wellness_date_format <- "%b %d %Y"
wellness_clean <-
  wellness_clean %>%
  arrange(desc(wellness_clean$date))

selectInput("date",
          label = NULL,
          choices = wellness_clean$date,
          selected = format(latest_wellness_date, 
                            format = wellness_date_format))


```

### Choose Athlete: 
```{r echo = FALSE}

selectizeInput("athlete",
            label = NULL,
            choices = wellness_clean$athlete,
            multiple = T,
            selected = "Athlete 8",
            options = list(maxItems = 1))

```

### Wellness Alert(s) 
### < 1.5 {data-height=200}
```{r echo = FALSE}


renderPrint({

alert <- 
  wellness_clean %>%
  filter(date == input$date) %>%
  select(date, athlete, sleep_quality_z, mood_z, readiness_to_train_z, soreness_z, stress_z, fatigue_z, sleep_hours_z) %>%
  gather(key = wellness_var, value = z_score, -c(date, athlete))

for (i in 1:length(alert$athlete)) {
   if (alert$z_score[[i]] < -1.5) {
  print(paste(alert$athlete[[i]], "-", alert$wellness_var[[i]]))
 } 
}

})

```

Row{.tabset .tabset-fade}
----------------------

### Wellness

```{r echo = FALSE}


renderPlot({
  
wellness_daily <- 
  wellness_clean %>%
  group_by(date, athlete) %>%
  filter(date == input$date)

wellness_individual <-
  wellness_clean %>%
  group_by(date, athlete) %>%
  filter(date == input$date,
         athlete == input$athlete) %>%
  select(date, athlete, sleep_quality_z, mood_z, readiness_to_train_z, soreness_z, stress_z, fatigue_z, sleep_hours_z) %>%
  rename(`Sleep Quality` = sleep_quality_z,
         Mood = mood_z,
         `Readiness to Train` = readiness_to_train_z,
         Soreness = soreness_z,
         Stress = stress_z,
         Fatigue = fatigue_z,
         `Sleep Hours` = sleep_hours_z) %>%
  gather(key = wellness_var, value = z_score, -c(date, athlete))

# Set ordering by daily_wellness_z
  wellness_daily$athlete <- reorder(wellness_daily$athlete, -wellness_daily$daily_wellness_z)
  
 all_individuals <- 
   ggplot(wellness_daily, aes(x = athlete, y = daily_wellness_z, fill = daily_wellness_z)) +
      geom_bar(stat = "identity", color = "black") +
      scale_fill_identity() +
      geom_rect(aes(ymin = -Inf, ymax = -1.5, xmin = -Inf, xmax = Inf), fill = "pink", alpha = 1/100) +
      geom_rect(aes(ymin = -1.5, ymax = 0, xmin = -Inf, xmax = Inf), fill = "yellow", alpha = 1/100) +
      geom_rect(aes(ymin = 0, ymax = Inf, xmin = -Inf, xmax = Inf), fill = "green", alpha = 1/100) +
      scale_fill_gradient2(low = "red", mid = "yellow", high = "green", midpoint = 0, limits = c(-3.0, 3.0), guide = F) +
      theme_minimal() +
      labs(title = "Daily Wellness",
           y = "Scaled Wellness < 0 is below their average",
           x = "") +
      coord_flip()
 
 # Set ordering by z_score
 wellness_individual$wellness_var <- reorder(wellness_individual$wellness_var, -wellness_individual$z_score)
 
 individual <-
  ggplot(wellness_individual, aes(x = wellness_var, y = z_score, fill = z_score)) +
      geom_bar(stat = "identity", color = "black") +
      scale_fill_identity() +
      geom_rect(aes(ymin = -Inf, ymax = -1.5, xmin = -Inf, xmax = Inf), fill = "pink", alpha = 1/100) +
      geom_rect(aes(ymin = -1.5, ymax = 0, xmin = -Inf, xmax = Inf), fill = "yellow", alpha = 1/100) +
      geom_rect(aes(ymin = 0, ymax = Inf, xmin = -Inf, xmax = Inf), fill = "green", alpha = 1/100) +
      scale_fill_gradient2(low = "red", mid = "yellow", high = "green", midpoint = 0, limits = c(-3.0, 3.0), guide = F) +
      theme_minimal() +
      labs(title = paste("Daily Wellness of", input$athlete),
           y = "Scaled Wellness < 0 is below their average",
           x = "") +
      coord_flip()
 
 grid.arrange(all_individuals, individual, nrow = 2)
  
 
})
  
```

### Training Load

```{r echo = FALSE}

DT::renderDataTable({

  load_table <-
    training_clean %>%
    filter(date == input$date) %>%
    select(athlete, team, injury_illness_status, training_availability, competition_load_z, practice_load_z, strength_load_z, conditioning_load_z)

  datatable(load_table, filter = "top", options = list(pageLength = 15),
            colnames = c("Athlete" = 2, "Team" = 3, "Injury/Illness Status" = 4, "Training Availability" = 5, 
                         "Competition TL" = 6, "Practice TL" = 7, "Strength TL" = 8, "Conditioning TL" = 9))

})

```
